Hierarchically modelling \emph{Kepler} dwarfs and subgiants to improve inference of stellar properties with asteroseismology

### 2020-10-29 paper/main.tex
Updated corner plots

In Figure \ref{fig:test-corners-np}, we show the joint posterior distributions for the hyperparameters of the PP model fit to the results of the NP model. We see that this method appears to recover the true values well. However, fitting the model this way does not benefit from the same uncertainty reduction on the stellar parameters as shown in the pooled models. Furthermore, the uncertainties on the individual stellar parameters were found to be unreliable due to boundary effects from the prior. This likely means that the uncertainties on the hyperparameter results for the NP model were underestimated.

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{../modelling/final_test_models/stars_results/test/corner_plot_truths.png}
    \caption{Corner plot showing the marginalised and joint posterior distributions between the NP model parameters for the synthetic stars. The true values are shown by the blue lines.}   
    \label{fig:test-corners-np} 
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{../modelling/final_test_models/population_results/test_100/population/corner_plot_truths.png}
    \caption{The same as Figure \ref{fig:test-corners-np} but for the PP model.}  
    \label{fig:test-corners-pp}   
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{../modelling/final_test_models/population_results/test_max_pool/population/corner_plot_truths.png}
    \caption{The same as Figure \ref{fig:test-corners-np} but for the MP model.}
    \label{fig:test-corners-mp} 
\end{figure}

>>>>

% In Figure \ref{fig:test-corners-np}, we show the joint posterior distributions for the hyperparameters of the PP model fit to the results of the NP model. We see that this method appears to recover the true values well. However, fitting the model this way does not benefit from the same uncertainty reduction on the stellar parameters as shown in the pooled models. Furthermore, the uncertainties on the individual stellar parameters were found to be unreliable due to boundary effects from the prior. This likely means that the uncertainties on the hyperparameter results for the NP model were underestimated.

% \begin{figure}
%     \centering
%     \includegraphics[width=\linewidth]{../modelling/final_test_models/stars_results/test/corner_plot_truths.png}
%     \caption{Corner plot showing the marginalised and joint posterior distributions between the NP model parameters for the synthetic stars. The true values are shown by the blue lines.}   
%     \label{fig:test-corners-np} 
% \end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{../modelling/final_test_models/population_results/test_100/population/corner_plot_truths.png}
    \caption{Corner plot showing the marginalised and joint posterior distributions between the PP model hyperparameters for 100 synthetic stars. The true values are shown by the blue lines.}  
    \label{fig:test-corners-pp}   
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{../modelling/final_test_models/population_results/test_max_pool/population/corner_plot_truths.png}
    \caption{The same as Figure \ref{fig:test-corners-pp} but for the MP model.}
    \label{fig:test-corners-mp} 
\end{figure}
